Pillar 1 - Sequential Pattern Mining

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
debug data prep for association rules

library(arules)
library(arulesSequences)
library(rlang)
```

@@

#Simple Rule Mining
##Data Exploration of Transcripts
```{r}

# For convenience
provide_statistics <- function(data){
  data %>%
    summarise(
      n      = n(),
      Min    = min(Grade),
      Max    = max(Grade), 
      Mean   = round(mean(Grade), 2), 
      Median = median(Grade), 
      SD        = round(sd(Grade), 2),
      Fail_rate = round(mean(Fail), 2),
      Fail_n = sum(Fail)
      )
}

@@

##Getting dates
For a first exploration of arules, we conceptualise our framework like this:
transaction = student
item = course

###Data preparation
First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.

```{r}
d_transactions <- d_course %>%
  select(Type, Code, Letters) %>%
  filter(Type == "Elective",
         ! Letters %in% c("SKI", "PRO"),
         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
  select(Code) %>%
  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
  select(`Student ID Number`, Code) %>%
  group_by(`Student ID Number`) %>%
  summarize(list_course = list(Code)) %>%
  group_by()

@@

We apply Apriori algorithm:
```{r}
results <- apriori(
  data = transactions, 
  parameter = list(
    supp = 0.02,
    smax = 1, # max support
    conf = 0.4,
    minlen = 2,
    maxlen = 2
    ),
  appearance = NULL,
  control = NULL
  ) %>%
  inspect

>>>>

library(arulesSequences)
```

@@

# Data Exploration

```{r statistic summary}

# For convenience
provide_statistics <- function(data){
  data %>%
    summarise(
      Min       = min(Grade),
      Max       = max(Grade), 
      Mean      = round(mean(Grade), 2), 
      Median    = median(Grade), 
      SD        = round(sd(Grade), 2),
      Fail_rate = round(mean(Fail), 2),
      Fail_n    = sum(Fail),
      n         = n()
      )
}

@@

# Association Rules
For a first exploration of arules, we conceptualise our framework like this:
transaction = student
item = course

## Creating Transactions
First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.

```{r AR data prep}
d_transactions <- d_course %>%

  # Exclude 
  filter(
    Type != "Mandatory",              # (i) mandatory courses e.g. COR, CAP, etc
    ! Letters %in% c("SKI", "PRO",    # (ii) skills & projects (taken by majority of students)
                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad
    ) %>%

  # Join with transcripts.
  left_join(d_transcript, by = "Course ID") %>%

  # Create transactions (student level)
  group_by(`Student ID`) %>%
    summarize(list_course = list(`Course ID`)) %>%
  ungroup

@@

## Apriori Algorithm
We apply Apriori algorithm:
```{r}
results <- apriori(
  data = transactions, 
  parameter = list(
    supp = 0.02,
    smax = 1, # max support
    conf = 0.4,
    minlen = 2,
    maxlen = 2
    ),
  appearance = NULL,
  control = NULL
  ) %>%
  inspect
